Stack Safety as a Security Property

### 2021-02-24 example1.tex
Narrowed example diagram
Example description to merge

Meanwhile confidentiality intuitively states that the callee, {\tt f}, is unaware
of the context of its call (with the exception, of course, of its arguments).
We state this in terms of noninterference: if we say ``components \(\components\)
interfere with the call to {\tt f},'' we mean that at some point up to when it returns,
{\tt f} would display different behavior if called from a state with a different
assignment of values to \(\components\). Here behavior encompasses uses of {\tt print},
return values, and changes to state that will persist beyond the return.
For instance, if {\tt f} computed the offset to access {\tt x} and branched on its value
to decide whether to double or triple its argument, a change in {\tt x} could translate
to a change in {\tt f}'s return value, making {\tt x} interfere with {\tt f}.

>>>>

Meanwhile confidentiality intuitively states that the callee, {\tt f}, is unaware
of the context of its call (with the exception, of course, of its arguments).
We state this in terms of noninterference: if we say ``components \(\components\)
interfere with {\tt f} up to its return,'' we mean that at some point up to when it returns,
{\tt f} would display different behavior if called from a state with a different
assignment of values to \(\components\). Here behavior encompasses uses of {\tt print},
return values, and changes to state that will persist beyond the return.
For instance, if {\tt f} computed the offset to access {\tt x} and branched on its value
to decide whether to double or triple its argument, a change in {\tt x} could translate
to a change in {\tt f}'s return value, making {\tt x} interfere with {\tt f}.
